Inferring Continuous and Discrete Population Genetic Structure Across Space

### 2017-09-15 writeup/conStruct.tex
fixed typos
more latexing

@@

% Use nameref to cite supporting information files (see Supporting Information section for more info)
\usepackage{nameref,hyperref}

% line numbers
\usepackage[right]{lineno}

@@

% Header and Footer with logo
\usepackage{lastpage,fancyhdr,graphicx}
\usepackage{epstopdf}
\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
\setlength{\headheight}{27.023pt}
\lhead{\includegraphics[width=2.0in]{latex/PLOS-submission.eps}}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\sf PLOS}

@@

\begin{figure}
	\centering
		{\includegraphics[width=4in,height=2.5in]{figs/schematic/method_schematic.png}}
		\caption{Schematic of our method, using $K=3$ as an example.
			     The pattern of isolation by distance within each layer is denoted by their color gradients, 
			     and $\phi^{(k)}$ denotes the covariance shared by samples with ancestry entirely in the $k$th layer.
			     Sampled populations on the landscape are inferred to be admixed between these layers; 
			     the $i$th sample draws proportion $w^{(k)}_i$ of its ancestry from layer $k$.
			     For convenience, each layer is depicted as a small square, but in fact, 
			     each layer exists everywhere in the sampled area,
			     so the small dashed circles on each layer show where 
			     the location of the highlighted admixed sample intersects each layer.
			    }\label{schematic}
\end{figure}

@@

\begin{figure}
	\centering
		{\includegraphics[width=6in,height=4in]{figs/sims/Fig2_simK1_sp_vs_nsp.pdf}}
	\caption{
	Map of admixture proportions estimated using the nonspatial model for $K=2$ through 4 (top row)
	and also the spatial model for $K=2$ through 4 (bottom row).
	The data were simulated using a single layer with nearest-neighbor symmetric migration between demes.
    }\label{simK1_pies}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=6in,height=2in]{figs/sims/sim_xvals.pdf}}
	\caption{
	Cross-validation results for data simulated under $K=1$, $K=2$, and $K=3$, 
	comparing the spatial and nonspatial \texttt{conStruct} models 
	(in blue and green, respectively) run with $K=1$ through 7.  
	The inset plots zoom in on cross-validation results outlined in the dotted boxes.
    }\label{sim_xvals}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=5in,height=2.5in]{figs/sims/simK1_laycon_barplots.pdf}}
		\caption{
			Layer/cluster contributions (i.e., how much total covariance is contributed by each layer/cluster), 
			for all layers estimated in runs using $K = 1$ through 7 
			for the spatial model (left),
			and for all clusters using the nonspatial model (right).
			Data were simulated using $K=1$.
			For each value of $K$ along the x-axis, there are an equal number of contributions plotted.
		}\label{simK1_laycon}
\end{figure}

@@

\begin{figure}
	\centering
		{\includegraphics[width=6in,height=4in]{figs/populus/pop_sp_results.pdf}}
	\caption{
	Maps of admixture proportions estimated for the \textit{Populus} dataset 
	using the spatial model for $K=2$ through 4 (a-c), 
	as well as the corresponding layer-specific covariance curves estimated under each model (d-f).
    }\label{populus_pies}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=6in,height=3in]{figs/populus/populus_std_xval.pdf}}
	\caption{
	Cross-validation results for \textit{Populus} dataset 
	comparing the spatial and nonspatial \texttt{conStruct} models run with $K=1$ through 7.  
	The first panel in each row shows all results; 
	the second panel zooms in on the results from analyses run with $K = 2$ through 7.
    }\label{populus_xvals}
\end{figure}

@@

\begin{figure}
	\centering
		{\includegraphics[width=6in,height=3in]{figs/bears/bears_sp_vs_nsp.pdf}}
	\caption{
	Maps of admixture proportions estimated for the black bear dataset 
	using the spatial model (left) and the nonspatial model (right) for $K=3$.
	Pies show mean admixture results across individuals within their diameter, 
	and the admixture results for all individuals included within each group are 
	shown in the plot above.
    }\label{bear_K3}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=6in,height=3in]{figs/bears/bear_std_xval.pdf}}
	\caption{
	Cross-validation results for black bear dataset 
	comparing the spatial and nonspatial \texttt{conStruct} models run with $K=1$ through 7.  
	The first panel in each row shows all results; 
	the second panel zooms in on the results from the spatial analyses run with $K = 4$ through 7.
    }\label{bear_xvals}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=6in,height=3in]{figs/bears/bears_laycon_barplots.pdf}}
	\caption{
	Layer/cluster contributions (i.e., how much total covariance is contributed by each layer/cluster), 
	for all layers estimated in runs using $K = 1$ through 7 
	for the spatial model (left),
	and for all clusters using the nonspatial model (right).
	For each value of $K$ along the x-axis, there are an equal number of contributions plotted.
	Colors are consistent with Fig \ref{bear_K3}.
    }\label{bear_laycon}
\end{figure}

@@

\newpage
\section*{Materials and Methods}

@@

\newpage
\section*{Cross validation}\label{Xvalidation}

@@

\newpage
\section*{Calculating layer contributions}\label{layer_contribution}

@@

\newpage
\section*{Simulation details}\label{sim_details}
We wished to simulate data under a model that had some biological realism, 
but at the same time had unambiguous true admixture proportions 
(so as to test the behavior of the method).
This second requirement precluded scenarios of, e.g, 
recent secondary contact between populations expanding out of different refugia, 
which would have more biological realism, 
but no unambiguous ancestry proportions for admixed populations.
Here, we describe in more detail the procedure we use to simulate our test dataset, 
using a cartoon schematic with $K=2$ as an example (Fig \ref{sim_setup}).

@@

\begin{figure}
	\centering
		{\includegraphics[width=4in,height=2.5in]{figs/sims/sim_setup.png}}
		\caption{Schematic of how we simulate datasets with continuous and discrete differentiation, using $K=2$ as an example.  
			    Going forward in time, the $K$ populations split from a common ancestor at time $\tau_{\text{s}}$,
			    then expand to each  colonize a lattice of demes with nearest-neighbor symmetric migration at time $\tau_{\text{e}}$,
			    then finally at time $\tau_{\text{a}}$ collapse into a single lattice consisting of demes 
			    with ancestry entirely in one or the other of the populations,
			    or admixed between them.
			    }\label{sim_setup}
\end{figure}

@@

\newpage
\begin{figure}
	\centering
		{\includegraphics[width=6in,height=4in]{figs/sims/simK1_nsp_pies.pdf}}
	\caption{
	Map of admixture proportions estimated using a nonspatial model for $K=2$ through 7.
	The data were simulated using one layer with nearest-neighbor symmetric migration between demes.
    }\label{simK1_nsp_pies}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=6in,height=4in]{figs/sims/simK1_sp_pies.pdf}}
	\caption{
	Map of admixture proportions estimated using a spatial model for $K=2$ through 7.
	The data were simulated using one layer with nearest-neighbor symmetric migration between demes.
    }\label{simK1_sp_pies}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=5in,height=2.5in]{figs/sims/simK1_std_xval.pdf}}
		\caption{
			Cross-validation results for data simulated under $K=1$,
			comparing the spatial and nonspatial \texttt{conStruct} models run with $K=1$ through 7.  
			The right panel zooms in on just the spatial cross-validation results.
		}\label{simK1_xval}
\end{figure}

\newpage
\begin{figure}
	\centering
		{\includegraphics[width=6in,height=4in]{figs/sims/simK2_nsp_pies.pdf}}
	\caption{
	Map of admixture proportions estimated using a nonspatial model for $K=2$ through 7.
	The data were simulated using two layers with nearest-neighbor symmetric migration between demes.
    }\label{simK2_nsp_pies}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=6in,height=4in]{figs/sims/simK2_sp_pies.pdf}}
	\caption{
	Map of admixture proportions estimated using a spatial model for $K=2$ through 7.
	The data were simulated using two layers with nearest-neighbor symmetric migration between demes.
    }\label{simK2_sp_pies}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=5in,height=2.5in]{figs/sims/simK2_laycon_barplots.pdf}}
		\caption{
			Layer/cluster contributions (i.e., how much total covariance is contributed by each layer/cluster), 
			for all layers estimated in runs using $K = 1$ through 7 
			for the spatial model (left), 
			and for all clusters using the nonspatial model (right).
			Data were simulated using $K=2$.
			For each value of $K$ along the x-axis, there are an equal number of contributions plotted.
		}\label{simK2_laycon}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=5in,height=2.5in]{figs/sims/simK2_std_xval.pdf}}
		\caption{
			Cross-validation results for data simulated under $K=2$,
			comparing the spatial and nonspatial \texttt{conStruct} models run with $K=1$ through 7.  
			The right panel zooms in on just the spatial cross-validation results.
		}\label{simK2_xval}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=4in,height=4in]{figs/sims/simK2_adprop_fit.pdf}}
		\caption{
			Plot of \texttt{conStruct} ability to correctly estimate admixture proportions on simulated data.
			Results are from an analysis with a spatial model using $K=2$.
		}\label{simK2_adprop_fit}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=6in,height=4in]{figs/sims/simK3_nsp_pies.pdf}}
	\caption{
	Map of admixture proportions estimated using a nonspatial model for $K=2$ through 7.
	The data were simulated using three layers with nearest-neighbor symmetric migration between demes.
    }\label{simK3_nsp_pies}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=6in,height=4in]{figs/sims/simK3_sp_pies.pdf}}
	\caption{
	Map of admixture proportions estimated using a spatial model for $K=2$ through 7.
	The data were simulated using three layers with nearest-neighbor symmetric migration between demes.
    }\label{simK3_sp_pies}
\end{figure}
\clearpage

\begin{figure}
	\centering
		{\includegraphics[width=5in,height=2.5in]{figs/sims/simK3_laycon_barplots.pdf}}
		\caption{
			Layer/cluster contributions (i.e., how much total covariance is contributed by each layer/cluster), 
			for all layers estimated in runs using $K = 1$ through 7 
			for the spatial model (left), 
			and for all clusters using the nonspatial model (right).
			Data were simulated using $K=3$.
			For each value of $K$ along the x-axis, there are an equal number of contributions plotted.
		}\label{simK3_laycon}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=5in,height=2.5in]{figs/sims/simK3_std_xval.pdf}}
		\caption{
			Cross-validation results for data simulated under $K=3$,
			comparing the spatial and nonspatial \texttt{conStruct} models run with $K=1$ through 7.  
			The right panel zooms in on just the spatial cross-validation results.
		}\label{simK3_xval}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=4in,height=4in]{figs/sims/simK3_adprop_fit.pdf}}
		\caption{
			Plot of \texttt{conStruct} ability to correctly estimate admixture proportions on simulated data.
			Results are from an analysis with a spatial model using $K=3$.
		}\label{simK3_adprop_fit}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=6in,height=2.25in]{figs/fastStr/fastStr_simK1_pies.pdf}}
	\caption{
	Map of admixture proportions estimated using fastSTRUCTURE \cite{fastStructure} for $K=2$ through 4.
	The data were simulated using one layer with nearest-neighbor symmetric migration between demes.
    }\label{fastStr_simK1}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=6in,height=2.25in]{figs/fastStr/fastStr_simK2_pies.pdf}}
	\caption{
	Map of admixture proportions estimated using fastSTRUCTURE \cite{fastStructure} for $K=2$ through 4.
	The data were simulated using two layers with nearest-neighbor symmetric migration between demes.
    }\label{fastStr_simK2}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=6in,height=2.25in]{figs/fastStr/fastStr_simK3_pies.pdf}}
	\caption{
	Map of admixture proportions estimated using fastSTRUCTURE \cite{fastStructure} for $K=2$ through 4.
	The data were simulated using three layers with nearest-neighbor symmetric migration between demes.
    }\label{fastStr_simK3}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=6in,height=5in]{figs/populus/populus_sampling_map.pdf}}
	\caption{
	Map of the sampled \textit{Populus} populations included in the analysis.
	The color of the sampling location denotes the putative species.
    }\label{populus_map}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=6in,height=4in]{figs/populus/populus_sp_pies.pdf}}
	\caption{
	Maps of admixture proportions estimated for the \textit{Populus} dataset 
	using the spatial model for $K=2$ through 7.
    }\label{populus_sp_pies}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=6in,height=4in]{figs/populus/populus_nsp_pies.pdf}}
	\caption{
	Maps of admixture proportions estimated for the \textit{Populus} dataset 
	using the nonspatial model for $K=2$ through 7.
    }\label{populus_nsp_pies}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=6in,height=4in]{figs/populus/populus_sp_layer_covs.pdf}}
	\caption{
	Plots showing the layer-specific parametric covariance IBD-curves 
	estimated for the \textit{Populus} data using 
	the spatial \texttt{conStruct} model run with $K=1$ through 6.
	Line colors are consistent with layer colors in Fig \ref{populus_sp_pies}.
	Points are colored by the species they are a covariance between:
	black on black points are sample covariances between populations of \textit{Populus balsamifera};
	green on black points are sample covariances between \bals{} and \tri{};
	green on green points are sample covariances between \tri{} and \tri{}.
    }\label{populus_sp_layer_covs}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=6in,height=4in]{figs/populus/populus_nsp_layer_covs.pdf}}
	\caption{
	Plots showing the cluster-specific parametric covariances 
	estimated for the \textit{Populus} data using 
	the nonspatial \texttt{conStruct} model run with $K=1$ through 6.
	Line colors are consistent with cluster colors in Fig \ref{populus_nsp_pies}.
	Points are colored by the species they are a covariance between:
	black on black points are sample covariances between populations of \textit{Populus balsamifera};
	green on black points are sample covariances between \bals{} and \tri{};
	green on green points are sample covariances between \tri{} and \tri{}.
    }\label{populus_nsp_layer_covs}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=6in,height=3in]{figs/populus/populus_laycon_barplots.pdf}}
	\caption{
	Layer/cluster contributions (i.e., how much total covariance is contributed by each layer/cluster), 
	for all layers estimated in runs using $K = 1$ through 7 
	for the spatial model (left), 
	and for all clusters using the nonspatial model (right).
	For each value of $K$ along the x-axis, there are an equal number of contributions plotted.
	Colors are consistent with Figs \ref{populus_sp_pies}, \ref{populus_sp_layer_covs}, \ref{populus_nsp_pies}, and \ref{populus_nsp_layer_covs}.
    }\label{populus_laycon}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=6in,height=4in]{figs/populus/poplar_fastStr_results.pdf}}
	\caption{
	Maps of admixture proportions estimated for the \textit{Populus} dataset 
	using fastSTRUCTURE \cite{fastStructure} for $K=2$ through 7.
    }\label{populus_fastStr}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=6in,height=4in]{figs/bears/bear_sp_results.pdf}}
	\caption{
	Map of admixture proportions estimated for the bear dataset 
	using the spatial model for $K=2$ through 7.
    }\label{bear_sp_pies}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=6in,height=4in]{figs/bears/bear_nsp_results.pdf}}
	\caption{
	Map of admixture proportions estimated for the bear dataset 
	using the nonspatial model for $K=2$ through 7.
    }\label{bear_nsp_pies}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=6in,height=4in]{figs/bears/bear_sp_layer_covs.pdf}}
	\caption{
	Plots showing the layer-specific parametric covariance IBD-curves 
	estimated for the black bear data using 
	the spatial \texttt{conStruct} model run with $K=1$ through 6.
	 }\label{bear_sp_layer_covs}
\end{figure}

>>>>

%% added PLR
\newif\ifsubmissionversion
\submissionversiontrue
\newif\ifincludesupplement
\includesupplementtrue
\newif\iffloatsatend
\floatsatendfalse

\iffloatsatend
\usepackage{endfloat}
\fi
%% end added PLR

@@

% Use nameref to cite supporting information files (see Supporting Information section for more info)
\usepackage{nameref}
\usepackage[hidelinks]{hyperref}

% line numbers
\ifsubmissionversion
\usepackage[right]{lineno}
\fi

@@

% Header and Footer with logo
\usepackage{lastpage,fancyhdr,graphicx}
\usepackage{epstopdf}
\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
\setlength{\headheight}{27.023pt}
\lhead{\includegraphics[width=\textwidth]{latex/PLOS-submission.eps}}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\sf PLOS}

@@

\begin{figure}
	\centering
		{\includegraphics[width=\textwidth]{figs/schematic/method_schematic.png}}
		\caption{Schematic of our method, using $K=3$ as an example.
			     The pattern of isolation by distance within each layer is denoted by their color gradients, 
			     and $\phi^{(k)}$ denotes the covariance shared by samples with ancestry entirely in the $k$th layer.
			     Sampled populations on the landscape are inferred to be admixed between these layers; 
			     the $i$th sample draws proportion $w^{(k)}_i$ of its ancestry from layer $k$.
			     For convenience, each layer is depicted as a small square, but in fact, 
			     each layer exists everywhere in the sampled area,
			     so the small dashed circles on each layer show where 
			     the location of the highlighted admixed sample intersects each layer.
			    }\label{schematic}
\end{figure}

@@

\begin{figure}
	\centering
		{\includegraphics[width=\textwidth]{figs/sims/Fig2_simK1_sp_vs_nsp.pdf}}
	\caption{
	Map of admixture proportions estimated using the nonspatial model for $K=2$ through 4 (top row)
	and also the spatial model for $K=2$ through 4 (bottom row).
	The data were simulated using a single layer with nearest-neighbor symmetric migration between demes.
    }\label{simK1_pies}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=\textwidth]{figs/sims/sim_xvals.pdf}}
	\caption{
	Cross-validation results for data simulated under $K=1$, $K=2$, and $K=3$, 
	comparing the spatial and nonspatial \texttt{conStruct} models 
	(in blue and green, respectively) run with $K=1$ through 7.  
	The inset plots zoom in on cross-validation results outlined in the dotted boxes.
    }\label{sim_xvals}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=\textwidth]{figs/sims/simK1_laycon_barplots.pdf}}
		\caption{
			Layer/cluster contributions (i.e., how much total covariance is contributed by each layer/cluster), 
			for all layers estimated in runs using $K = 1$ through 7 
			for the spatial model (left),
			and for all clusters using the nonspatial model (right).
			Data were simulated using $K=1$.
			For each value of $K$ along the x-axis, there are an equal number of contributions plotted.
		}\label{simK1_laycon}
\end{figure}

@@

\begin{figure}
	\centering
		{\includegraphics[width=\textwidth]{figs/populus/pop_sp_results.pdf}}
	\caption{
	Maps of admixture proportions estimated for the \textit{Populus} dataset 
	using the spatial model for $K=2$ through 4 (a-c), 
	as well as the corresponding layer-specific covariance curves estimated under each model (d-f).
    }\label{populus_pies}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=\textwidth]{figs/populus/populus_std_xval.pdf}}
	\caption{
	Cross-validation results for \textit{Populus} dataset 
	comparing the spatial and nonspatial \texttt{conStruct} models run with $K=1$ through 7.  
	The first panel in each row shows all results; 
	the second panel zooms in on the results from analyses run with $K = 2$ through 7.
    }\label{populus_xvals}
\end{figure}

@@

\begin{figure}
	\centering
		{\includegraphics[width=\textwidth]{figs/bears/bears_sp_vs_nsp.pdf}}
	\caption{
	Maps of admixture proportions estimated for the black bear dataset 
	using the spatial model (left) and the nonspatial model (right) for $K=3$.
	Pies show mean admixture results across individuals within their diameter, 
	and the admixture results for all individuals included within each group are 
	shown in the plot above.
    }\label{bear_K3}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=\textwidth]{figs/bears/bear_std_xval.pdf}}
	\caption{
	Cross-validation results for black bear dataset 
	comparing the spatial and nonspatial \texttt{conStruct} models run with $K=1$ through 7.  
	The first panel in each row shows all results; 
	the second panel zooms in on the results from the spatial analyses run with $K = 4$ through 7.
    }\label{bear_xvals}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=\textwidth]{figs/bears/bears_laycon_barplots.pdf}}
	\caption{
	Layer/cluster contributions (i.e., how much total covariance is contributed by each layer/cluster), 
	for all layers estimated in runs using $K = 1$ through 7 
	for the spatial model (left),
	and for all clusters using the nonspatial model (right).
	For each value of $K$ along the x-axis, there are an equal number of contributions plotted.
	Colors are consistent with Fig \ref{bear_K3}.
    }\label{bear_laycon}
\end{figure}

@@

\section*{Materials and Methods}

@@

\section*{Cross validation}\label{Xvalidation}

@@

\section*{Calculating layer contributions}\label{layer_contribution}

@@

\section*{Simulation details}\label{sim_details}
We wished to simulate data under a model that had some biological realism, 
but at the same time had unambiguous true admixture proportions 
(so as to test the behavior of the method).
This second requirement precluded scenarios of, e.g, 
recent secondary contact between populations expanding out of different refugia, 
which would have more biological realism, 
but no unambiguous ancestry proportions for admixed populations.
Here, we describe in more detail the procedure we use to simulate our test dataset, 
using a cartoon schematic with $K=2$ as an example (Fig \ref{sim_setup}).

@@

\begin{figure}
	\centering
		{\includegraphics[width=\textwidth]{figs/sims/sim_setup.png}}
		\caption{Schematic of how we simulate datasets with continuous and discrete differentiation, using $K=2$ as an example.  
			    Going forward in time, the $K$ populations split from a common ancestor at time $\tau_{\text{s}}$,
			    then expand to each  colonize a lattice of demes with nearest-neighbor symmetric migration at time $\tau_{\text{e}}$,
			    then finally at time $\tau_{\text{a}}$ collapse into a single lattice consisting of demes 
			    with ancestry entirely in one or the other of the populations,
			    or admixed between them.
			    }\label{sim_setup}
\end{figure}

We thank Marjorie Weber, Yaniv Brandvain, William Wetzel, 
Mariah Meek, Doc Edge, and Matthew Stephens 
for invaluable comments on the method and manuscript, 
as well as Quentin Cronk, who provided input on the \textit{Populus} analyses, 
and Emily Puckett, who provided input on the black bear analyses.
We also thank the attendees at the 2017 SSE Meeting in Portland, OR, 
whose votes determined the name of the method.
% This work was supported in part by 
% the National Science Foundation under award number NSF \#1262645 (DBI) to PR and GC, 
% the National Institute of General Medical Sciences of the National
% Institutes of Health under award numbers NIH R01-GM108779 to GC,
% and the National Science Foundation under award numbers NSF \#1148897 and \#1402725 to GB.

%%% BEGIN IF INCLUDE SUPPLEMENT
\ifincludesupplement

@@

% \linespread{1}
\iffloatsatend
\processdelayedfloats
\fi

\newpage
\begin{figure}
	\centering
		{\includegraphics[width=\textwidth]{figs/sims/simK1_nsp_pies.pdf}}
	\caption{
	Map of admixture proportions estimated using a nonspatial model for $K=2$ through 7.
	The data were simulated using one layer with nearest-neighbor symmetric migration between demes.
    }\label{simK1_nsp_pies}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=\textwidth]{figs/sims/simK1_sp_pies.pdf}}
	\caption{
	Map of admixture proportions estimated using a spatial model for $K=2$ through 7.
	The data were simulated using one layer with nearest-neighbor symmetric migration between demes.
    }\label{simK1_sp_pies}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=\textwidth]{figs/sims/simK1_std_xval.pdf}}
		\caption{
			Cross-validation results for data simulated under $K=1$,
			comparing the spatial and nonspatial \texttt{conStruct} models run with $K=1$ through 7.  
			The right panel zooms in on just the spatial cross-validation results.
		}\label{simK1_xval}
\end{figure}

\newpage
\begin{figure}
	\centering
		{\includegraphics[width=\textwidth]{figs/sims/simK2_nsp_pies.pdf}}
	\caption{
	Map of admixture proportions estimated using a nonspatial model for $K=2$ through 7.
	The data were simulated using two layers with nearest-neighbor symmetric migration between demes.
    }\label{simK2_nsp_pies}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=\textwidth]{figs/sims/simK2_sp_pies.pdf}}
	\caption{
	Map of admixture proportions estimated using a spatial model for $K=2$ through 7.
	The data were simulated using two layers with nearest-neighbor symmetric migration between demes.
    }\label{simK2_sp_pies}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=\textwidth]{figs/sims/simK2_laycon_barplots.pdf}}
		\caption{
			Layer/cluster contributions (i.e., how much total covariance is contributed by each layer/cluster), 
			for all layers estimated in runs using $K = 1$ through 7 
			for the spatial model (left), 
			and for all clusters using the nonspatial model (right).
			Data were simulated using $K=2$.
			For each value of $K$ along the x-axis, there are an equal number of contributions plotted.
		}\label{simK2_laycon}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=\textwidth]{figs/sims/simK2_std_xval.pdf}}
		\caption{
			Cross-validation results for data simulated under $K=2$,
			comparing the spatial and nonspatial \texttt{conStruct} models run with $K=1$ through 7.  
			The right panel zooms in on just the spatial cross-validation results.
		}\label{simK2_xval}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=\textwidth]{figs/sims/simK2_adprop_fit.pdf}}
		\caption{
			Plot of \texttt{conStruct} ability to correctly estimate admixture proportions on simulated data.
			Results are from an analysis with a spatial model using $K=2$.
		}\label{simK2_adprop_fit}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=\textwidth]{figs/sims/simK3_nsp_pies.pdf}}
	\caption{
	Map of admixture proportions estimated using a nonspatial model for $K=2$ through 7.
	The data were simulated using three layers with nearest-neighbor symmetric migration between demes.
    }\label{simK3_nsp_pies}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=\textwidth]{figs/sims/simK3_sp_pies.pdf}}
	\caption{
	Map of admixture proportions estimated using a spatial model for $K=2$ through 7.
	The data were simulated using three layers with nearest-neighbor symmetric migration between demes.
    }\label{simK3_sp_pies}
\end{figure}
\clearpage

\begin{figure}
	\centering
		{\includegraphics[width=\textwidth]{figs/sims/simK3_laycon_barplots.pdf}}
		\caption{
			Layer/cluster contributions (i.e., how much total covariance is contributed by each layer/cluster), 
			for all layers estimated in runs using $K = 1$ through 7 
			for the spatial model (left), 
			and for all clusters using the nonspatial model (right).
			Data were simulated using $K=3$.
			For each value of $K$ along the x-axis, there are an equal number of contributions plotted.
		}\label{simK3_laycon}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=\textwidth]{figs/sims/simK3_std_xval.pdf}}
		\caption{
			Cross-validation results for data simulated under $K=3$,
			comparing the spatial and nonspatial \texttt{conStruct} models run with $K=1$ through 7.  
			The right panel zooms in on just the spatial cross-validation results.
		}\label{simK3_xval}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=\textwidth]{figs/sims/simK3_adprop_fit.pdf}}
		\caption{
			Plot of \texttt{conStruct} ability to correctly estimate admixture proportions on simulated data.
			Results are from an analysis with a spatial model using $K=3$.
		}\label{simK3_adprop_fit}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=\textwidth]{figs/fastStr/fastStr_simK1_pies.pdf}}
	\caption{
	Map of admixture proportions estimated using fastSTRUCTURE \cite{fastStructure} for $K=2$ through 4.
	The data were simulated using one layer with nearest-neighbor symmetric migration between demes.
    }\label{fastStr_simK1}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=\textwidth]{figs/fastStr/fastStr_simK2_pies.pdf}}
	\caption{
	Map of admixture proportions estimated using fastSTRUCTURE \cite{fastStructure} for $K=2$ through 4.
	The data were simulated using two layers with nearest-neighbor symmetric migration between demes.
    }\label{fastStr_simK2}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=\textwidth]{figs/fastStr/fastStr_simK3_pies.pdf}}
	\caption{
	Map of admixture proportions estimated using fastSTRUCTURE \cite{fastStructure} for $K=2$ through 4.
	The data were simulated using three layers with nearest-neighbor symmetric migration between demes.
    }\label{fastStr_simK3}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=\textwidth]{figs/populus/populus_sampling_map.pdf}}
	\caption{
	Map of the sampled \textit{Populus} populations included in the analysis.
	The color of the sampling location denotes the putative species.
    }\label{populus_map}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=\textwidth]{figs/populus/populus_sp_pies.pdf}}
	\caption{
	Maps of admixture proportions estimated for the \textit{Populus} dataset 
	using the spatial model for $K=2$ through 7.
    }\label{populus_sp_pies}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=\textwidth]{figs/populus/populus_nsp_pies.pdf}}
	\caption{
	Maps of admixture proportions estimated for the \textit{Populus} dataset 
	using the nonspatial model for $K=2$ through 7.
    }\label{populus_nsp_pies}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=\textwidth]{figs/populus/populus_sp_layer_covs.pdf}}
	\caption{
	Plots showing the layer-specific parametric covariance IBD-curves 
	estimated for the \textit{Populus} data using 
	the spatial \texttt{conStruct} model run with $K=1$ through 6.
	Line colors are consistent with layer colors in Fig \ref{populus_sp_pies}.
	Points are colored by the species they are a covariance between:
	black on black points are sample covariances between populations of \textit{Populus balsamifera};
	green on black points are sample covariances between \bals{} and \tri{};
	green on green points are sample covariances between \tri{} and \tri{}.
    }\label{populus_sp_layer_covs}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=\textwidth]{figs/populus/populus_nsp_layer_covs.pdf}}
	\caption{
	Plots showing the cluster-specific parametric covariances 
	estimated for the \textit{Populus} data using 
	the nonspatial \texttt{conStruct} model run with $K=1$ through 6.
	Line colors are consistent with cluster colors in Fig \ref{populus_nsp_pies}.
	Points are colored by the species they are a covariance between:
	black on black points are sample covariances between populations of \textit{Populus balsamifera};
	green on black points are sample covariances between \bals{} and \tri{};
	green on green points are sample covariances between \tri{} and \tri{}.
    }\label{populus_nsp_layer_covs}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=\textwidth]{figs/populus/populus_laycon_barplots.pdf}}
	\caption{
	Layer/cluster contributions (i.e., how much total covariance is contributed by each layer/cluster), 
	for all layers estimated in runs using $K = 1$ through 7 
	for the spatial model (left), 
	and for all clusters using the nonspatial model (right).
	For each value of $K$ along the x-axis, there are an equal number of contributions plotted.
	Colors are consistent with Figs \ref{populus_sp_pies}, \ref{populus_sp_layer_covs}, \ref{populus_nsp_pies}, and \ref{populus_nsp_layer_covs}.
    }\label{populus_laycon}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=\textwidth]{figs/populus/poplar_fastStr_results.pdf}}
	\caption{
	Maps of admixture proportions estimated for the \textit{Populus} dataset 
	using fastSTRUCTURE \cite{fastStructure} for $K=2$ through 7.
    }\label{populus_fastStr}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=\textwidth]{figs/bears/bear_sp_results.pdf}}
	\caption{
	Map of admixture proportions estimated for the bear dataset 
	using the spatial model for $K=2$ through 7.
    }\label{bear_sp_pies}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=\textwidth]{figs/bears/bear_nsp_results.pdf}}
	\caption{
	Map of admixture proportions estimated for the bear dataset 
	using the nonspatial model for $K=2$ through 7.
    }\label{bear_nsp_pies}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=\textwidth]{figs/bears/bear_sp_layer_covs.pdf}}
	\caption{
	Plots showing the layer-specific parametric covariance IBD-curves 
	estimated for the black bear data using 
	the spatial \texttt{conStruct} model run with $K=1$ through 6.
	 }\label{bear_sp_layer_covs}
\end{figure}

\begin{figure}
	\centering
		{\includegraphics[width=\textwidth]{figs/bears/bear_nsp_layer_covs.pdf}}
	\caption{
	Plots showing the cluster-specific parametric covariances 
	estimated for the black bear data using 
	the nonspatial \texttt{conStruct} model run with $K=1$ through 6.
    }\label{bear_nsp_layer_covs}
\end{figure}
